When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-02-28 doc/paper/vpd_et_paper.tex
simplify scatter plot to just do derivative d_et/d_vpd?

\subsection{Testing VPD$_{crit}$}
As stated in the above discussion of ENF, we are mostly interested in the critical threshold $VPD_{crit}$ for which the sign of the ET response to VPD ($\frac{\partial \; ET}{\partial \; VPD}$) is determined. When VPD is less than VPD$_{crit}$, ET response to VPD is negative ($\frac{\partial \; ET}{\partial \; VPD}  < 0$), i.e. plant response dominates, and when VPD is greater than VPD$_{crit}$, ET response to VPD is positive  ($\frac{\partial \; ET}{\partial \; VPD} > 0$). i.e. atmospheric demand dominates. Theoretically, this $VPD_{crit}$ is mostly a function of PFT and not of climate. This $VPD_{crit}$, and how it compares with environmental VPD and water supply, will exert a strong control on species selection in competitive environments.

>>>>

\subsection{Observed ET response to VPD}
As stated in the above discussion of ENF, we are mostly interested in the critical threshold $VPD_{crit}$ for which the sign of the ET response to VPD ($\frac{\partial \; ET}{\partial \; VPD}$) is determined. When VPD is less than VPD$_{crit}$, ET response to VPD is negative ($\frac{\partial \; ET}{\partial \; VPD}  < 0$), i.e. plant response dominates, and when VPD is greater than VPD$_{crit}$, ET response to VPD is positive  ($\frac{\partial \; ET}{\partial \; VPD} > 0$). i.e. atmospheric demand dominates. Theoretically, this $VPD_{crit}$ is mostly a function of PFT and not of climate. This $VPD_{crit}$, and how it compares with environmental VPD and water supply, will exert a strong control on species selection in competitive environments.
